Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-06-10 Journal1/Response3/Response.tex

% % % % % % % % % % % % % % % Reviewer 2 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 2} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The Reviewer would like to thank the authors for their revision of the paper with respect to the comments and suggestions in the previous submission. Whereas the authors have considered parts of the suggestions and improved specific areas of the work, there are still a lot of remaining issues of concern in the current version of the paper. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing
thoughtful comments, and offering constructive suggestions that strengthened and enhanced its
quality. We hope that the responses provided herein can alleviate the reviewer’s concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``While the authors have taken into consideration the Reviewer’s comments about the re-structuring of the Introduction, I am afraid that the current version is not in the adequate state for publication. Initially, the paragraphs of the Introduction have no logical connection among them. It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable. 
We changed the introduction and add it below

Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.). Network slicing can provide resource isolation for various services, increasing the system's efficiency. This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services. The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.

Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on QoS, each service requires its slice of the network.
The eMBB service fulfills the demand for high capacity and throughput. Moreover, the URLLC service offers autonomous vehicles, tactile internet, remote surgery services, and other high-quality and low latency services. However, mMTC comprises a large number of internet of things (IoT) devices that transmit small payloads
[1]–[6].
Nevertheless, the existing radio access network (RAN) architecture lacks adequate flexibility and openness to manage these demands for various services simultaneously. Therefore, development in RAN architecture is needed to support these requirements for different services simultaneously. Open radio access network (O-RAN) is the new RAN generation introduced to deal with these issues.
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

The hardware is decoupled from the software in the O-RAN architecture, and each component is implemented as a virtual network function (VNF) that can be deployed on a virtual machine (VM) or container. 
Virtual network functions (VNF) are system function blocks in network function virtualization (NFV) systems. The concept of NFV refers to the separation of network software and hardware elements. Therefore network functions can run on commodity hardware. The NFV technology offers to execute VNFs as VMs or containers on a cloud environment [7], [8].
As a result, some O-RAN components defined in section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit O-DU, and RAN Intelligent Controller (RIC)-near real-time, are near real-time virtualized and implemented as VNFs. VNFs can also be deployed as virtual machines (VMs) or containers.

This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the number of VNFs is also taken into account to reduce latency, especially for URLLC services.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary. I would definitely suggest to move that as a background Section. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} `` Furthermore, it is surprising how the Introduction does not contain a single research challenge. Why is the problem relevant at all? Why do you even need to study this problem and why is it hard to solve? ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We add the motivation subsection and answer these questions in it. Below we rewrite this section.

The studies in  [9]–[11] have investigated resource allocation in C-RAN by considering the limitation on power and delay, respectively. However, this architecture is inefficient whenever we have different services with different QoS simultaneously. Additionally, RAN slicing requires a more flexible and open architecture. Therefore, we need a new architecture that supports slicing to implement RAN slicing for various services. O-RAN architecture has emerged as
a new architecture that can serve different services simultaneously using RAN slicing. In [2], the RAN slicing is considered for C-RAN architecture for eMBB and URLLC. Nevertheless, the authors did not consider latency for URLLC, which is the main property of the URLLC. 
Moreover, the authors did not consider the weakness of C-RAN architecture.
In [12], the authors examine the total delay of the UE in the O-RAN architecture. However, the paper did not consider the different services and other QoS.

Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously. 
Therefore, we want to study the problem of obtaining the optimal number of VNF, RB assignments, and power allocation to maximize the system's throughput and guarantee the QoS of services. This problem is mixed-integer non-linear programming. Hence, it is difficult to solve and requires some relaxation, convexification, and other methods for obtaining the sub-optimal solution presented in the following sections.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment4:} `` In turn, in the main contributions subsection, the initial sentences of almost all contribution paragraphs cannot be considered as contributions. For instance:

1) “We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.”
2) “ Different services need to consider varying QoS conditions, including delay, power, and throughput.”
3) “The main problem is mixed-integer non-linear programming that is extremely difficult to solve.”
''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We removed these sentences and rewrite the contribution. Below we write the changes.

In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
\begin{itemize}
\item The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC. We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.
\item The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.
\item We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation. For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\item We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method. Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.
\end{itemize}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I changed the background from sub-section to the section part.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague. It is still not clear how this process is achieved and how it is linked to their method. I was expecting at least a connection or introduction to Fig.1 where the system is shown. Additionally, more information with respect to the interaction with the system would have been required in that regard. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}

### 2022-06-13 Journal1/paper5TNSM/pr.tex
last version

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, and Saeede Parsaeefard$^\dagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. Due to O-RAN, flexibility, openness, and lower operational costs will be possible. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing to isolate different types of services.
The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
Nevertheless, we break it down into two different steps where an iterative algorithm finds a near-optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
The proposed method is validated via simulations that illustrate a higher data rate and lower end-to-end delay than existing methods.
\end{abstract}
\begin{IEEEkeywords}
Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing.
\end{IEEEkeywords}
\section{Introduction}
%\subsection{State Of The Arts}
\textcolor{MidnightBlue}{Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.). Network slicing can provide resource isolation for various services, increasing the system's efficiency. This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services. The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.}

>>>>

\title{ Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}
}
%%%%%%%%%%%%%%%
%\author{\IEEEauthorblockN{ Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{School of ECE} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{ Saeedeh Parsaeefard}
%\IEEEauthorblockA{\textit{Department of ECE} \\
%\textit{University of Toronto}\\
%Toronto, Canada \\
%saeede.parsaeefard@gmail.com}
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \author{
%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-mansouri}
%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%    Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir,
%    \vspace{-.2cm}
%  }
%\author{Mojdeh Karbalaee Motalleb,~\IEEEmembership{University of Tehran,}
%        Vahid Shah-mansouri,~\IEEEmembership{University of Tehran,}
%        and~Saeede Parsaeefard,~\IEEEmembership{University of Toronto}% <-this % stops a space
%}
\author{\small Mojdeh Karbalaee Motalleb$^*$, Vahid Shah-Mansouri$^*$, Saeede Parsaeefard$^\dagger$, and Onel Luis Alcaraz López$^\ddagger$ \\ Email: \{mojdeh.karbalaee, vmansouri\}@ut.ac.ir, \{saeede.parsaeefard\}@gmail.com, \{onel.alcarazlopez\}@oulu.fi\\
\IEEEauthorblockA{$^*$School of ECE, University of Tehran, Tehran, Iran, $^\dagger$University of Toronto, Toronto, Canada, $^\ddagger$University of Oulu, Oulu, Finland}
 }
\maketitle
\pagenumbering{gobble}
%\vspace*{-4em}
\begin{abstract}
%\vspace*{-1.5em}
Taking advantage of virtual radio access networks (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. Due to O-RAN, flexibility, openness, and lower operational costs will be possible. O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing to isolate different types of services.
The limited fronthaul capacity and the restriction of end-to-end delay are considered at the same time.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is a mixed-integer non-linear programming problem that is non-trivial to solve numerically.
Nevertheless, we break it down into two different steps where an iterative algorithm finds a near-optimal solution.
In the first step, we reformulate and simplify the problem to find the power allocation, PRB assignment, and the number of VNFs. In the second step, the O-RU association is achieved.
The proposed method is validated via simulations that illustrate a higher data rate and lower end-to-end delay than existing methods.
\end{abstract}
\begin{IEEEkeywords}
Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing.
\end{IEEEkeywords}
\section{Introduction}
%\subsection{State Of The Arts}
\textcolor{MidnightBlue}{Network slicing is the most effective solution for 5G wireless cellular networks to achieve the desired level of QoS (i.e., quality, delay, power, etc.). Network slicing can provide resource isolation for various services, increasing the system's efficiency. This architecture has several implementations, including core slicing, radio access network (RAN) slicing, and both for different 5G services. The network slicing concept has the potential to serve multiple services with varying architectures and quality of service (QoS) requirements.}
